%-------------------------
% Resume in Latex
% Author : Sahaj Saliya
% License : MIT
%------------------------

\documentclass[a4paper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNH}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\resumeSubHeadingListStartBullets}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\usepackage{array}
\makeatletter
\newcommand\HUGE{\@setfontsize\Huge{38}{47}} 
\newcolumntype{L}{>{\hb@xt@\z@\bgroup}l<{\hss\egroup}}
\newcolumntype{C}{>{\centering\arraybackslash}c}
\newcolumntype{R}{>{\hb@xt@\z@\bgroup\hss}r<{\egroup}}
\makeatother

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{L@{\extracolsep{\fill}}C@{\extracolsep{\fill}}R}
  {} & \multirow{2}{*}{\Huge \textbf{Sahaj Saliya}} & {} \\
  {sahajsaliya.59.2015@gmail.com} &
  {} &
  {Github: SahajIVVIX-1} \\
  {(+91)-9016151812} & {} & {Linkedin: sahajs59} \\

\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Pandit Deendayal Energy University - PDEU (Formerly PDPU)}{Gandhinagar, GJ}
      {B.Tech in Information \& Communication Technology (ICT), \textbf{GPA: 8.0/10.0}}{June 2023 -- May 2027}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

% -------------------- Project 1 --------------------
\resumeSubheading
    {DCGAN Modernization \& Analytics Pipeline}{GitHub}
    {Generative AI \& Post-Training Diagnostics}{2026}
    \resumeItemListStart
      \resumeItemNH{Implemented a high-stability Generative Adversarial Network (GAN) using 2018-2022 training paradigms including Label Smoothing and D-Dropout to stabilize the Nash Equilibrium between the Generator and Discriminator.}
      \resumeItemNH{Developed a professional post-training analytics dashboard that automates evaluation through confidence histograms ($D(x)$ vs $D(G(z))$) and real-time visualization of learned edge/texture detectors.}
      \resumeItemNH{\textbf{Tech Stack:} PyTorch, Torchvision, Python 3, Advanced Convolutions, Latent Space Analytics, Data Visualization.}
    \resumeItemListEnd

% -------------------- Project 2 --------------------
\resumeSubheading
    {SentinelProxy Suite}{GitHub}
    {Secure Network Gateways · Traffic Intelligence}{2025}
    \resumeItemListStart
      \resumeItemNH{Developed an AI-enhanced HTTPS proxy and DNS resolver featuring real-time traffic inspection, role-based access control (RBAC), and dynamic blocklist enforcement.}
      \resumeItemNH{Automated Windows network orchestration via PowerShell and integrated a modular Node.js backend with SQLite for persistent auditing and logging.}
      \resumeItemNH{\textbf{Tech Stack:} Node.js, Socket.IO, SQLite, http-proxy, node-forge, PowerShell, JavaScript.}
    \resumeItemListEnd

% -------------------- Project 3 --------------------
\resumeSubheading
    {Microplastic Detection \& Data Management System}{}
    {Visual Intelligence · Automated Environmental Analysis}{2025}
    \resumeItemListStart
      \resumeItemNH{Trained and fine-tuned a \textbf{YOLOv11} object detection model to detect microplastic particles from visual data, optimizing it to classify microplastics while estimating particle size under varying imaging conditions.}
      \resumeItemNH{\textbf{Tech Stack:} Python, LLM, YOLOv11, PyTorch, OpenCV, CUDA, NumPy, Computer Vision.}
    \resumeItemListEnd

% -------------------- Project 4 --------------------
\resumeSubheading
    {Python Script-Based Projects}{GitHub}
    {Productivity Automation · Developer-Centric Tooling}{2023 -- 2024}
    \resumeItemListStart
      \resumeItemNH{\textbf{Smaran – Smart Desktop Reminder}, a PyQt6-based Windows application featuring animated notifications and advanced scheduling logic for productivity automation.}
      \resumeItemNH{\textbf{PyEnv Launcher}, a unified graphical interface to manage Python projects, virtual environments (venv/conda), dependency isolation, and Git-based workflows.}
      \resumeItemNH{\textbf{Digital Hand Cricket Game}, implementing complete gameplay mechanics, scoring rules, and deterministic tie-breaker logic via console-based interaction.} 
      \resumeItemNH{\textbf{Tech Stack:} Python, PyQt6, JSON, CSV, Virtual Environments, Git, Windows Registry, Console I/O.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EXTRACURRICULARS-----------------
\section{Involvement}
\resumeSubHeadingListStartBullets

\resumeSubItem{IEEE Conference Paper Presentations}
{Presented two IEEE research papers \textbf{on behalf of the author teams} at the \textbf{2nd IEEE Conference on AIMV}, held on 16--17 August 2025. The presentations covered \textit{Deepfake Audio Detection using Deep Learning} and \textit{Intelligent Cognitive Frameworks for Crime Prediction in Smart Cities}. The papers are published on IEEE Xplore (DOI: 10.1109/AIMV66517.2025.11203307 \& DOI: 10.1109/AIMV66517.2025.11203581).}

\resumeSubItem{Hackathon Participation}
{Participated in the \textbf{Code4Cause Hackathon 2024}, a national-level hackathon held in Delhi, collaborating in a team-based environment to design \& implement technology-driven solutions under strict time constraints.}

\resumeSubItem{Technical Workshop – Vertex AI \& Firebase}
{Attended a hands-on session by the \textbf{Google Developer Group (GDG) Gandhinagar}, working with \textbf{Vertex AI} to fine-tune a model and generate research insights using the \textbf{Gemini 1.5 Pro} model, while also gaining practical experience with \textbf{Firebase} for application development.}

\resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
\resumeSubHeadingListStart

\resumeSubItem{Programming \& Core Tools}
{Python (Advanced), SQL, MATLAB, NumPy, Pandas, Scikit-Learn}

\resumeSubItem{Machine Learning \& AI}
{Deep Learning, Reinforcement Learning (RL), Large Language Models (LLMs), EDA, Probability \& Statistics, Linear Algebra, PyTorch}

\resumeSubItem{System Design \& Backend}
{Scalable System Design, REST APIs (Flask), Model Deployment, Microservices, JSON Data Pipelines}

\resumeSubItem{Cloud \& DevOps}
{AWS, Google Cloud, Docker, Linux, Git/GitHub}

\resumeSubItem{Data Visualization}
{Power BI, Excel (VBA), Matplotlib, Seaborn}

\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------------
\section{Certifications}
\resumeSubHeadingListStartBullets
\resumeSubItem{Deep Learning}
{NPTEL – IIT Ropar, \textbf{Score: 66\%}}

\resumeSubItem{AI/ML for Geodata Analysis}
{IISRO-IIRS (ISRO) – Applied AI/ML to satellite imagery and geospatial data.}

\resumeSubItem{Code4Cause Hackathon 2.0}
{National-level hackathon participation, solving real-world technology problems under time constraints.}

\resumeSubItem{Signal Processing Onramp}
{Applied MATLAB to real-world signal processing, visualization, and data analysis.}
\resumeSubHeadingListEnd
    
%-------------------------------------------
\end{document}